---
title: "Project"
author: "Div, Anant, Simran, Amir"
date: "28/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries
```{r lib, echo=FALSE}
library(rms)
df <- data.frame(read_excel("Attrition Sample 11.xlsx"))
```



## If you have any categorical variables coded as numeric, you need to convert them to a factor to indicate that they should be treated as a categorical variable in the model
```{r factor, echo=FALSE}
df$BusinessTravel <- factor(df$BusinessTravel)
df$Department <- factor(df$Department)
df$EducationField <- factor(df$EducationField)
df$Gender <- factor(df$Gender)
df$JobRole <- factor(df$JobRole)
df$JobLevel <- factor(df$JobLevel)
df$Education <- factor(df$Education)
df$JobSatisfaction <- factor(df$JobSatisfaction)
df$PerformanceRating <- factor(df$PerformanceRating)
df$Attrition <- factor(df$Attrition)
df$WorkLifeBalance <- factor(df$WorkLifeBalance)

df$Age = as.numeric(as.character(df$Age))
df$DailyRate = as.numeric(as.character(df$DailyRate))
df$YearsSinceLastPromotion = as.numeric(as.character(df$YearsSinceLastPromotion))
df$YearsWithCurrManager = as.numeric(as.character(df$YearsWithCurrManager))
df$MonthlyIncome = as.numeric(as.character(df$MonthlyIncome))
df$MonthlyRate = as.numeric(as.character(df$MonthlyRate))
df$PercentSalaryHike = as.numeric(as.character(df$PercentSalaryHike))
df$TrainingTimesLastYear = as.numeric(as.character(df$TrainingTimesLastYear))
```

# Get a quick description of your data
```{r descdata, echo=FALSE}
d <- describe(df)
html(d, size = 80, scroll = TRUE)
```

## Produce a two-way contingency table of some predictors and outcome
## This helpd to ensure there are not 0 cells
## If any cell has 0 - then collapse that category
```{r catplot, echo=FALSE}
# This works only on categorical xs
# chocolate is y
# Not rejecting on the basis of this - mention in report
xtabs(~Attrition + BusinessTravel, data = df) #Should include for now
xtabs(~Attrition + Department, data = df) #Maybe not
xtabs(~Attrition + EducationField, data = df) # No
xtabs(~Attrition + Gender, data = df) # Try putting it - check significance
xtabs(~Attrition + Education, data = df) # Nope
xtabs(~Attrition + JobSatisfaction, data = df) # Definitely
xtabs(~Attrition + PerformanceRating, data = df) # This would've been a good observation
# but we only have data for employees with rating of 3 and above (Excellent and Outstanding)
# that causes bias
xtabs(~Attrition + JobLevel, data = df) #Seems significant, confirm if higher number refers to a higher posn
xtabs(~Attrition + JobRole, data = df) #Try - and check significance and then vif test to check colinearity with Work Life Balance - Simran's favourite
xtabs(~Attrition + WorkLifeBalance, data = df) # Include
# Finally we are taking - BusinessTravel, JobSatisfaction, WorkLifeBalance
```

## Would be overly predictive or it would just be an identifier, eg Employee id - these things would have 
## no bearing on the model, ignore constants also, pick reasonable predictors - based on 
## rational reasons - 
## Prepare the data
## We need to select our potential predictor variables?
```{r selectpred, echo=FALSE}
# List of names of variables to analyze
v <- c('Attrition','BusinessTravel','Department','EducationField','Gender',
       'Education', 'JobSatisfaction', 'PerformanceRating', 'JobLevel', 'JobRole', 
       'Age', 'DailyRate', 'YearsSinceLastPromotion', 'YearsWithCurrManager',
       'MonthlyIncome', 'MonthlyRate', 'PercentSalaryHike', 'TrainingTimesLastYear',
       'WorkLifeBalance')
sel <- df[, v]

sel$Attrition <- case_when (
  sel$Attrition == 'Yes' ~ 1,
  df$Attrition == 'No' ~ 0,
)
```


# Summarize the data more formally
```{r summarize, echo=FALSE}
s <- summary(BusinessTravel + Department + EducationField + Gender + Education + 
             JobSatisfaction + PerformanceRating + JobLevel + JobRole + Age + 
             DailyRate +  YearsSinceLastPromotion + YearsWithCurrManager + MonthlyIncome
             + MonthlyRate + PercentSalaryHike + TrainingTimesLastYear + WorkLifeBalance
             ~ Attrition, data = sel, overall = TRUE)


html(s, caption='Predictors according to Attrition(Y/N)',
     exclude1 = TRUE, npct = 'both', digits = 2,
     prmsd = TRUE, brmsd = TRUE, msdsize = mu$smaller2)
```





# Visualize the relationship between the continuous variables and the outcome to assess linearity

# Histspike bins the continuous x variable into equal-width bins and then computes and plots the frequency counts of Y within each bin. The function then displays the proportions as a vertical histogram with a loess curve fit to the plot.The loess nonparametric smoother is an excellent tool for determining the shape of the relationship between a predictor and the response
```{r seelin, echo=FALSE}
# datadist function computes statistical summaries of predictors to  automate 
# estimation and plotting of effects
dd <- datadist(sel)
options(datadist = "dd")

# Graph for Age
a <- ggplot(sel, aes(x = Age, y = Attrition)) +
  histSpikeg(Attrition ~ Age, lowess = TRUE, data = sel) +
  labs(x = "\nAge", y = "Probability(Attrition)\n")

a


# Graph for WorkLifeBalance
a <- ggplot(sel, aes(x = WorkLifeBalance, y = Attrition)) +
  histSpikeg(Attrition ~ WorkLifeBalance, lowess = TRUE, data = sel) +
  labs(x = "\nWorkLifeBalance", y = "Probability(Attrition)\n")


a <- ggplot(sel, aes(x = WorkLifeBalance, y = Attrition)) +
  histSpikeg(Attrition ~ WorkLifeBalance, lowess = TRUE, data = sel) +
  labs(x = "\nWorkLifeBalance", y = "Probability(Attrition)\n")

a
```


# Finally we are taking - BusinessTravel, JobSatisfaction, WorkLifeBalance, PercentHike (Cont)
 
# Consider polynomial transformations for possible non-linearity
```{r seepoly, echo=FALSE}
quad_hike <- lrm(Attrition ~ BusinessTravel + JobSatisfaction + WorkLifeBalance + poly(PercentSalaryHike, 3), data = sel)
print(quad_hike)
```
## It's clear - 
# Consider a sex by age interaction
```{r seeinter, echo=FALSE}
# Finally we are taking - BusinessTravel, JobSatisfaction, WorkLifeBalance, PercentHike (Cont)
log_mod <- lrm(Attrition ~ BusinessTravel + JobSatisfaction + WorkLifeBalance + pol(PercentSalaryHike,2), data = sel, x=TRUE, y= TRUE)

print(log_mod)
```